---
title: "assignemnt "
author: "swetha"
date: "`r Sys.Date()`"
output: html_document
---

We will now try to predict per capita crime rate in the Boston data set. 

a) Try out some of the regression methods explored in this chapter,such as best subset 
selection, the lasso, ridge regression, and PCR. Present and discuss results for the 
approaches that you consider. 



```{r}
library(MASS)
data("Boston")
library(leaps)
library(glmnet)
library(pls)
```
```{r}
boston=Boston
```

```{r}
fit.lm=lm(crim~.,data = boston) 
summary(fit.lm) 
```
In this model We zn,dis,rad,black,medv are having relationship with response variable. 

```{r}
best_subset=regsubsets(crim~.,data = boston,nvmax = 13) 
best_subset.summary<-summary(best_subset) 
best_subset.summary$adjr2 
```
```{r}
par(mfrow = c(1, 3)) 
```

```{r}
plot(best_subset.summary$cp, xlab = "Number of Variables", ylab = "C_p", type = "l") 
points(which.min(best_subset.summary$cp), best_subset.summary$cp[which.min(best_subset.summary$cp)], col = "green", cex = 3, pch = 20) 
```
```{r}
plot(best_subset.summary$bic, xlab = "Number of Variables", ylab = "BIC", type = "l") 
points(which.min(best_subset.summary$bic), best_subset.summary$bic[which.min(best_subset.summary$bic)], col = "green", cex = 3, pch = 20) 

```
```{r}
plot(best_subset.summary$adjr2, xlab = "Number of Variables", ylab = "Adjusted R-squared", type = "l") 
points(which.max(best_subset.summary$adjr2), best_subset.summary$adjr2[which.max(best_subset.summary$adjr2)], col = "green", cex = 3, pch = 20)
```
```{r}
coef(best_subset,which.min(best_subset.summary$cp)) 
```
```{r}
set.seed(2) 
boston_matrix=model.matrix(crim~.,data = boston)[,-1]
```


```{r}
ridge=cv.glmnet(boston_matrix,boston$crim,alpha=0) 
bestlam<-ridge$lambda.min 
bestlam
```
```{r}
coef(ridge,s=bestlam)
```
```{r}

set.seed(1) 
lasso=cv.glmnet(boston_matrix,boston$crim,alpha=1) 
bestlam<-lasso$lambda.min 
bestlam 
```
```{r}
coef(lasso,s=bestlam)
```
```{r}
set.seed(2) 
pcr=pcr(crim~.,data=boston,scale=TRUE,validation="CV") 
pcr_summary<- summary(pcr) 
```
```{r}
validationplot(pcr,val.type = "MSEP")
```
```{r}
load_pcr<-pcr$loadings[,1:8] 
load_pcr 
```

b) Propose a model (or set of models) that seem to perform well on this data set, and 
justify your answer. Make sure that you areevaluating model performance using 
validation set error, crossvalidation, or some other reasonable alternative, as 
opposed to using training error. 

```{r}
train_boston = sample(nrow(boston), nrow(boston) * 0.70) 
tr_boston = boston[train_boston, ] 
te_boston = boston[-train_boston, ] 

set.seed(3) 
tr_boston_matrix = model.matrix(crim ~ ., data = tr_boston)[, -1] 
te_boston_matrix = model.matrix(crim ~ ., data = te_boston)[, -1] 


ridge = cv.glmnet(tr_boston_matrix, tr_boston$crim, alpha = 0) 


bestlam = ridge$lambda.min 


print(bestlam)

```
```{r}
pred_ridge=predict(ridge,s=bestlam,newx = te_boston_matrix) 
test_error=mean((te_boston$crim- pred_ridge)^2) 
test_error 
```
```{r}
rmse= sqrt(test_error) 
(rmse/mean(te_boston$crim))*100 
```

```{r}
lasso=cv.glmnet(tr_boston_matrix,tr_boston$crim,alpha=1) 
bestlam=lasso$lambda.min 
lasso_pred = predict(lasso, s = bestlam, newx = te_boston_matrix) 
test_error = mean((te_boston$crim - lasso_pred)^2) 
test_error 
```
```{r}
rmse_lasso= sqrt(test_error) 
(rmse_lasso/mean(te_boston$crim))*100
```
c) Does your chosen model involve all of the features in the data set? Why or why not?

The chosen model does not involve all of the features in the data set, because some of the 
predictors are not statistically significant to response.


