---
title: "Ass-4"
author: "swetha"
date: "`r Sys.Date()`"
output: html_document
---

1.We continue to consider the use of a logistic regression model to predict the probability 
Of  default using income and balance on the Default data set. In particular, we will now 
compute estimates for the standard errors of the income and balance logistic regression
coefficients in two different ways: (1) using the bootstrap, and (2) using the standard 
formula for computing the standard errors in the glm() function. Do not forget to set a 
random seed before beginning your analysis

(a) Using the summary() and glm() functions, determine the estimated standard errors for the coefficients associated with income and balance in a multiple logistic regression model that uses both predictors.
```{r}
library(ISLR)
data("Default")
default=Default 
```

```{r}
fit=glm(default~income+balance,data = default,family = binomial) 
summary(fit) 
```
balance has high standard error and income has small standart error compare to balance.


b) Write a function, boot.fn(), that takes as input the Default data set as well as an 
index of the observations, and that outputs the coefficient estimates for income and 
balance in the multiple logistic regression model. 

```{r}
boot.fn=function(data,index){ 
  b.fit=glm(default~income+balance,data=data,family = binomial,subset = index) 
  return(coef(b.fit)) 
} 
```


c) Use the boot() function together with your boot.fn() function to estimate the 
standard errors of the logistic regression coefficients for income and balance. 
```{r}
library(boot) 
set.seed(1) 
boot(default,boot.fn,100)
```

d) Comment on the estimated standard errors obtained using the glm() function and 
using your bootstrap function. 


```{r}
0.000004985-0.000004186088       
0.0002274-0.000226242  
```
The difference between the results from the glm and the bootstrap method for income is 
very small (0.000000798912). For balance the difference is slightly larger 
(0.000001158).the estimated standard errors from the two methods differ, with the 
bootstrap method providing lower standard errors compared to glm. 





2.	we saw that the cv.glm() function can be used in order to compute the LOOCV test error 
	estimate. Alternatively, one could compute those quantities using just the glm() and 
	predict.glm() functions, and a for loop. You will now take this approach in order to 
	compute the LOOCV error for a simple logistic regression model on the Weekly data set.
	
(a) Fit a logistic regression model that predicts Direction using Lag1 and Lag2.

```{r}
library(ISLR)
data("Weekly")
week=Weekly

```

```{r}
fit1=glm(Direction~Lag1+Lag2,data=week,family = binomial) 
summary(fit1) 
```
b) Fit a logistic regressionmodel that predicts Direction using Lag1 and Lag2 using all 
but the first observation. 

```{r}
fit2=glm(Direction~Lag1+Lag2,data = week[-1,],family = binomial) 
summary(fit2) 
```
c) Use the model from (b) to predict the direction of the first observation. 

```{r}
pred=predict(fit2,week[1,],type = "response")>0.5 
week$Direction[1] 

```
We predict the Direction to be UP; the true Direction was DOWN. 


d) Write a for loop from i = 1 to i = n, where n is the number of observations in the data 
set, that performs each of the following steps: Fit a logistic regression model using 
all but the ith observation to predict Direction using Lag1 and Lag2.  Compute the 
posterior probability of the market moving up for the ith observation.  Use the 
posterior probability for the ith observation in order to predict whether or not the 
market moves up.  Determine whether or not an error was made in predicting the 
direction for the ith observation. If an error was made, then indicate this as a 1, and 
otherwise indicate it as a 0.  

```{r}
count = rep(0, dim(week)[1]) 
for (i in 1:(dim(week)[1])) { 
    glm.fit = glm(Direction ~ Lag1 + Lag2, data = week[-i, ], family = binomial) 
    is_up = predict.glm(glm.fit, week[i, ], type = "response") > 0.5 
    is_true_up = week[i, ]$Direction == "Up" 
    if (is_up != is_true_up)  
        count[i] = 1 
} 
sum(count)
```
e) Take the average of the n numbers obtained in (d)iv in order to obtain the LOOCV 
estimate for the test error. Comment on the results. 

```{r}
mean(count)
```
The LOOCV average test error is 44.9%. It is high.
